Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-09 discussion.tex
...

>>>>

- Performance. We have provided a mechanism for measuring performance, and showed a glimpse into the overhead imposed by the first version of the Dashboard. For our case study the overhead is acceptable, but for performance critical applications, it might be too large. One of the downsides of the current implementation is the fact that the dashboard runs in the same process as the main application and that Python only supports green threads. The performance could be greatly improved if instead the Dashboard would be run in a different process, and the information would be posted to it by using a messaging service. However, that would complicate the installation and configuration, and for this kind of architecture, there are also other alternatives.

- We designed the dashboard to make it easy to adopt. However, we still have to run a study on the challenges and opportunities of the adoption of such a dashboard.
